Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-14 paper.tex

The pool architecture is overall the most scalable, which is not
surprising since it is designed precisely for scalability. Tight
integration is the least scalable and all the other architectures
perform the same overall. The global scalability score, however,
should not conceal \closednote{Naj}{what do you mean by
  mask?}{Tristan}{I guess 'hide' or 'conceal' are better
  words. Fixed.} the unique characteristics of architectures regarding
this criterion. Nested workflows are the only architecture that can
easily accommodate distributed workflow execution, which can be
critical in some cases. At the same time, the scheduling constraints
created by task encapsulation and nested workflows may become problematic \closednote{Naj}{please don't use these from-film-marketing
  words?! :-) }{Tristan}{OK!} depending on the type of targeted
infrastructure. Non-reliable infrastructures\closednote{Naj}{you mean by
  the showstoppers, i.e. the nested workflows which can accommodate
  distributed executions but are limited by scheduling constraints?}{Tristan}{Yes. I rephrased a bit this part.} ,
for example, could hardly cope with workflow engines being wrapped in
computing tasks as done in task encapsulation. The availability of
multiple engine instances could also become a critical feature for
science gateways with important workloads, which would favor task
encapsulation and pool. \note{Naj}{I feel this paragraph is a bit
  vague, and doesn't distill and contextualize the thorough work
  described before.}

Differences in other specific features should not be neglected. Nested
workflows (with service invocation) and workflow import (with service
invocation) are the only architectures that support meta-workflows;
task encapsulation and nested workflows may hamper
fine-grained debugging. \closednote{Rafael}{I would suggest to provide
  some more examples when this could be interesting.}{Tristan}{Done.}
The availability of fine-grained debugging information may also be
critical to efficient user support.

@@

A few limitations should be considered when using the results of our
evaluation. First, our evaluation methods aimed to provide comparative
metrics, however the high-level of abstraction used to derive these
metrics hinders the complexity of real systems to some
extent.\closednote{Naj}{Here, you were bashing your article harshly,
  so I rewrote it}{Tristan}{yup, thanks!} In particular, the
presented architectures are abstract patterns that may be mixed
together in actual systems.\answerednote{Naj}{something about "theoretical
  pattern", and "blending" is jarring, are these common words in the
  computer sci context?}{Tristan}{Better now?} The distinction between tight integration and
service invocation, for instance, may not always be that clear in
practice. Service invocation may also be combined with task
encapsulation in some cases. However, the criteria discussed in this
work would still apply to broadly compare and categorize such cases of
hybrid architectures.

>>>>

The pool architecture is overall the most scalable, which is not
surprising since it is designed precisely for scalability. Tight
integration is the least scalable and all the other architectures
perform the same overall. The global scalability score, however,
should not conceal \closednote{Naj}{what do you mean by
  mask?}{Tristan}{I guess 'hide' or 'conceal' are better
  words. Fixed.} the unique characteristics of architectures regarding
this criterion. Nested workflows are the only architecture that can
easily accommodate distributed workflow execution, which can be
critical in some cases. At the same time, the scheduling constraints
created by task encapsulation and nested workflows may become problematic \closednote{Naj}{please don't use these from-film-marketing
  words?! :-) }{Tristan}{OK!} depending on the type of targeted
infrastructure. Non-reliable infrastructures\closednote{Naj}{you mean by
  the showstoppers, i.e. the nested workflows which can accommodate
  distributed executions but are limited by scheduling constraints?}{Tristan}{Yes. I rephrased a bit this part.},
for example, could hardly cope with workflow engines being wrapped in
computing tasks as done in task encapsulation. The availability of
multiple engine instances could also become a critical feature for
science gateways with important workloads, which would favor task
encapsulation and pool. \note{Naj}{I feel this paragraph is a bit
  vague, and doesn't distill and contextualize the thorough work
  described before.}

Differences in other specific features should not be neglected. Nested
workflows (with service invocation) and workflow import (with service
invocation) are the only architectures that support meta-workflows. Besides,
task encapsulation and nested workflows may hamper
fine-grained debugging. \closednote{Rafael}{I would suggest to provide
  some more examples when this could be interesting.}{Tristan}{Done.}
The availability of fine-grained debugging information may also be
critical to efficient user support.

@@

A few limitations should be considered when using the results of our
evaluation. First, our evaluation methods aimed to provide comparative
metrics, however the high-level of abstraction used to derive these
metrics hinders the complexity of real systems to some
extent.\closednote{Naj}{Here, you were bashing your article harshly,
  so I rewrote it}{Tristan}{yup, thanks!} In particular, the
presented architectures are abstract patterns that may be mixed
together in actual systems.\closednote{Naj}{something about "theoretical
  pattern", and "blending" is jarring, are these common words in the
  computer sci context?}{Tristan}{Better now?} The distinction between tight integration and
service invocation, for instance, may not always be that clear in
practice. Service invocation may also be combined with task
encapsulation in some cases. However, the criteria discussed in this
work would still apply to broadly compare and categorize such cases of
hybrid architectures.
